Blowship - Untraceable Instantaneous Message Transfer via a Central Server

### 2014-03-12 paper.tex
Updated stuff

\documentclass[twocolumn]{paper}
\usepackage{comment}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{cite}
\usepackage{relsize}
\usepackage[margin=1.0in]{geometry}

@@

In this paper we present a centralized anonymity system that uses a single, untrusted central server, adapting decentralized p2p protocols to work in this context, and combine these with Computational Private Information Retrieval (CPIR) to enable low-latency, low-overhead anonymous communication. The primary reason behind a centeral server is to have a browser based service which needs a server to initialze the peer to peer network.

@@

Traditional cryptography obsucres the message being sent from one party to another. This is useful for many purposes but there is an important aspect of your communication that is freely availble to anyone observing the transfer: who the message is being sent to. Much work has been done to build networks that can obscure message passing by esentially mixing the messages around in a large group of peers in such a way that a peer in the network, or even a large group of peers cannot figure out where the message is going to end up. Many of these system rely upon the fact that the user is accessing a constantly avaible resource, such as with tor\cite{tor}, or in the case of email one can wait as long as nessesary for a message to be read by the user on the other end.

@@

\item[Private Information Retrieval] PIR has been used to facilitate anonymous communication in a variety of ways. The Pynchon Gate \cite{wpes2005} is a nym system that uses information-theoretic PIR as a layer of indirection between a user and their nym - allowing users to retrieve mail sent to their nym with information-theoretic privacy guarantees. Tor-PIR \cite{TODO} uses PIR to distribute information about servers without forcing users to download the entire directory.

@@

\begin{figure}[ht]
  \includegraphics[width=230px]{PSP.png}
  \caption{A simple pseudo-p2p circuit}
\end{figure}

\subsection{Basic Protocol}
Assume that Alice has obtained Bob's public key and unique ID while maintaining her anonymity. Assume also that Alice can obtain the public keys and IDs for $n \le N$ peers at random while hiding her choice from Surge.

@@

In this system, peers operate exactly as MIXes in the literature \cite{chaum-mix} . That is, they prevent traffic correlation by removing a layer of encryption, prevent relay attacks [[[soething]]], as well (as we will discuss) by reordering and batching messages. 
\subsection{Adversaries}
In this context, we have several distinct types of adversaries we must consider:
\begin{enumerate}
  \item\textbf{Penguin.} Penguin is any Peer who can intercept and alter messages being passed through it. 
  \item\textbf{Surge.} Surge is a compromised central Server. He can alter and intercept any messages passing through, and can provide bogus information to any peer.
  \item\textbf{Proletariat.} The Proletariat is a group of colluding Penguins.
  \item\textbf{The Palace.} The Palace is a collusion of the Proletariat and Surge.
\end{enumerate}
\subsection{Security Flaws}
Here we'll perform a simplified analysis of the security flaws of the basic, naive system described so far. 
Let $P_{AB}$ be the probability that Alice sent a given message that was delivered to to Bob. 
\begin{enumerate}
\item\textbf{Linear Chain.} If we assume that Alice's message is the only message sent by any of $P_1 ... P_n$, $Surge$ can determine that $P_{AB} > (n+1)^{-1} \gg 1/N$. This is because Surge knows that one of $A \cup \{P_1 ... P_n\}$ talked to Bob.
\item\textbf{Collusion.} If  $s$ peers collude with Surge to form the Palace, then the Palace can determine on average (depending on which peers Alice picked), that $P_{AB} > (n/(N-s)+1)^{-1}$ - that is, Alice has a chance $1 - (N-s)/N$ of each peer being compromised and not contributing to her privacy.
\item\textbf{Timing.} Even if $P_1 ... P_n$ are sending other messages, if Surge knows the probability distribution of the peer delay between receiving a message and forwarding it, he can discover the increased probability that Alice and Bob are talking. 
\item\textbf{Multiple Communications.} If Alice sends another message to Bob, or Bob back to Alice, the chance that they are communicating increases even more. 
\item\textbf{Man in the Middle.} If Alice acquries Bob's public key from Surge (and vice-versa), there's nothing to stop Surge from mounting a Man in the Middle attack given this simple model. 
\end{enumerate}
This is fairly poor security. If Alice chooses $n = 5$, then if her chosen peers send no other messages until hers is delivered, Surge knows $P_{AB} > 1/6$ chance that Alice is talking to Bob. If $60\%$ of peers are part of the Palace, then Surge possibly knows $P_{AB} = 1$ if $n \subset s$, but the expectation is $E[P_{AB}] = 1/3$.

@@

If we assume that there is not a Palace, then Alice needs only choose $n = log(N)$, If every node sends 2 messages at once, and her message passes through $log(N)$ nodes, then there are $2^n = N$ possible messages that Alice sent, and hopefully $N$ possible destinations. The likelihood is that in $log(N)$ steps from Alice, there will be less than $2^n$ unique recipients of messages, but we can adjust for this by increasing the number of nodes $n$ we choose. If every node has an average unique branching factor of $z$ rather than $2$, we can just set $n = log_z(N)$ and then $z^{log_z(N)} = 1/N$. Then, the $size$ of Alice's anonymity probability distribution is $\approx 1$ since the sender probabilities are roughly uniform.

@@

\subsection{The Palace} Assuming the set $S$ peers colludes with the server where $s = |S| > n$, and Alice chooses her circuit $C$ of peers randomly (where $|C| = n$), there is unfortunately some chance that $R \subset S$ and so $P_{AB} = 1$. If $s = \phi*N$ peers are part of the palace, on average $E[P_{AB}] = 2^{-\phi log(N)}$. The chance Surge can tell with probability $> \gamma$ that Alice and Bob are talking to eachother, $p(P_{AB} > \gamma)$ requires Alice choosing $x$ Palace members as peers.

@@

>>>>

\documentclass[twocolumn]{paper}
\usepackage{comment}
\usepackage{authblk}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{cite}
\usepackage{relsize}
\usepackage[margin=1.0in]{geometry}

@@

In this paper we present a centralized anonymity system that uses a single, untrusted central server, adapting decentralized peer-to-peer (p2p) protocols to work in this context, and combine these with Computational Private Information Retrieval (CPIR) to enable low-latency, low-overhead anonymous communication. The primary reason behind a centeral server is to have a browser based service which needs a server to initialze the peer to peer network.

@@

Traditional cryptography obsucres the message being sent from one party to another. This is useful for many purposes but there is an important aspect of your communication that is freely availble to anyone observing the transfer: who the message is being sent to. Much work has been done to build networks that can obscure message passing by esentially mixing the messages around in a large group of peers in such a way that a peer in the network, or even a large group of peers cannot figure out where the message is going to end up. Many of these system rely upon the fact that the user is accessing a constantly avaible resource, such as with tor\cite{tor-design}, or in the case of email one can wait as long as nessesary for a message to be read by the user on the other end.

@@

\item[Private Information Retrieval] PIR has been used to facilitate anonymous communication in a variety of ways. The Pynchon Gate \cite{sassaman:wpes2005} is a nym system that uses information-theoretic PIR as a layer of indirection between a user and their nym - allowing users to retrieve mail sent to their nym with information-theoretic privacy guarantees. Tor-PIR \cite{TODO} uses PIR to distribute information about servers without forcing users to download the entire directory.

@@

\begin{figure}[ht]
\begin{center}
\begin{tikzpicture}[scale=0.2]
\tikzstyle{every node}+=[inner sep=0pt]
\draw [black] (15.3,-22.1) circle (3);
\draw (15.3,-22.1) node {$Peer_a$};
\draw [black] (22.7,-22.1) circle (3);
\draw (22.7,-22.1) node {$S_1$};
\draw [black] (30,-22.1) circle (3);
\draw (30,-22.1) node {$Peer_b$};
\draw [black] (37.2,-22.1) circle (3);
\draw (37.2,-22.1) node {$S_2$};
\draw [black] (44.5,-22.1) circle (3);
\draw (44.5,-22.1) node {$Peer_c$};
\draw [black] (18.3,-22.1) -- (19.7,-22.1);
\fill [black] (19.7,-22.1) -- (18.9,-21.6) -- (18.9,-22.6);
\draw [black] (25.7,-22.1) -- (27,-22.1);
\fill [black] (27,-22.1) -- (26.2,-21.6) -- (26.2,-22.6);
\draw [black] (33,-22.1) -- (34.2,-22.1);
\fill [black] (34.2,-22.1) -- (33.4,-21.6) -- (33.4,-22.6);
\draw [black] (40.2,-22.1) -- (41.5,-22.1);
\fill [black] (41.5,-22.1) -- (40.7,-21.6) -- (40.7,-22.6);
\end{tikzpicture}
\end{center}
  \caption{A simple pseudo-p2p circuit}
\end{figure}

\subsection{Adversaries}
In this context, we have several distinct types of adversaries we must consider:
\begin{description}
\item[Penguin] 
  is any Peer who can intercept any messages and modify the content of that message.
\item[Surge] 
   is a compromised central Server. He can alter and intercept any messages passing through, and can provide bogus information to any peer.
\item[Proletariat] 
  is a group of colluding Penguins.
\item[The Fort] 
  is Surge and penguins colluding. 
\end{description}

\subsection{Basic Protocol}
Assume that Alice has obtained Bob's public key and unique ID while maintaining her anonymity. This could be done using a public keyserver of some kind, or perhaps they have exchanged keys in advance through some other channel. Assume also that Alice can obtain the public keys and IDs for $n \le N$ peers at random while hiding her choice from Surge.

@@

In this system, peers operate exactly as MIXes in the literature \cite{chaum-mix} . That is, they prevent traffic correlation by removing a layer of encryption, prevent relay attacks [[[soething]]], as well (as we will discuss) by reordering and batching messages. 
\subsection{Security Flaws}
Here we'll perform a simplified analysis of the security flaws of the basic, naive system described so far. 
Let $P_{AB}$ be the probability that Alice sent a given message that was delivered to to Bob. 
\begin{enumerate}
\item\textbf{Linear Chain.} If we assume that Alice's message is the only message sent by any of $P_1 ... P_n$, $Surge$ can determine that $P_{AB} > (n+1)^{-1} \gg 1/N$. This is because Surge knows that one of $A \cup \{P_1 ... P_n\}$ talked to Bob.
\item\textbf{Collusion.} If  $s$ peers collude with Surge to form the Fort, then the Fort can determine on average (depending on which peers Alice picked), that $P_{AB} > (n/(N-s)+1)^{-1}$ - that is, Alice has a chance $1 - (N-s)/N$ of each peer being compromised and not contributing to her privacy.
\item\textbf{Timing.} Even if $P_1 ... P_n$ are sending other messages, if Surge knows the probability distribution of the peer delay between receiving a message and forwarding it, he can discover the increased probability that Alice and Bob are talking. 
\item\textbf{Multiple Communications.} If Alice sends another message to Bob, or Bob back to Alice, the chance that they are communicating increases even more. 
\item\textbf{Man in the Middle.} If Alice acquries Bob's public key from Surge (and vice-versa), there's nothing to stop Surge from mounting a Man in the Middle attack given this simple model. 
\end{enumerate}
This is fairly poor security. If Alice chooses $n = 5$, then if her chosen peers send no other messages until hers is delivered, Surge knows $P_{AB} > 1/6$ chance that Alice is talking to Bob. If $60\%$ of peers are part of the Fort, then Surge possibly knows $P_{AB} = 1$ if $n \subset s$, but the expectation is $E[P_{AB}] = 1/3$.

@@

If we assume that there is not a Fort, then Alice needs only choose $n = log(N)$, If every node sends 2 messages at once, and her message passes through $log(N)$ nodes, then there are $2^n = N$ possible messages that Alice sent, and hopefully $N$ possible destinations. The likelihood is that in $log(N)$ steps from Alice, there will be less than $2^n$ unique recipients of messages, but we can adjust for this by increasing the number of nodes $n$ we choose. If every node has an average unique branching factor of $z$ rather than $2$, we can just set $n = log_z(N)$ and then $z^{log_z(N)} = 1/N$. Then, the $size$ of Alice's anonymity probability distribution is $\approx 1$ since the sender probabilities are roughly uniform.

@@

\subsection{The Fort} Assuming the set $S$ peers colludes with the server where $s = |S| > n$, and Alice chooses her circuit $C$ of peers randomly (where $|C| = n$), there is unfortunately some chance that $R \subset S$ and so $P_{AB} = 1$. If $s = \phi*N$ peers are part of the fort, on average $E[P_{AB}] = 2^{-\phi log(N)}$. The chance Surge can tell with probability $> \gamma$ that Alice and Bob are talking to eachother, $p(P_{AB} > \gamma)$ requires Alice choosing $x$ Fort members as peers.

@@

\section{Conclusion}
Conclusion words here about our network which is basically whatever we have in the introduction
